Stochastic Approximation Monte Carlo with a Dynamic Update Factor

### 2019-11-08 papers/histogram/sad.tex
change to plot maximum error rather than mean for LJ31
add plot of C_V with converged result

@@

\subsection{Lennard-Jones clusters with 38 atoms}

>>>>

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/lj-cv-error}
  \caption{The maximum error in the heat capacity of the LJ31 cluster
    in the temperature range from 0.01~$\epsilon/k_B$ to
    0.1~$\epsilon/k_B$.}
  \label{fig:lj-cv-error}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/lj-cv}
  \caption{The heat capacity of the LJ31 cluster after $10^{12}$ moves
    as calculated with each method.}
  \label{fig:lj-cv}
\end{figure}

@@

The heat capacity changes significantly even at these low temperatures
when the size of the cavity is increased.  We use a 2.5 cavity because
``everyone else'' does.
